Visualize ukb whole genome, using ctwas results

### 2023-05-25 analysis/simulation-ctwas-ukbWG-gtex.adipose_visual.Rmd
PVEgene=0.02

>>>>

## Results from `L=1` vs `L=5` for low SNP PVE settings.

```{r sim 2, out.width = "98%", out.height="95%"}
outputdir <- "~/causalTWAS/simulations/simulation_ctwas_rss_20230322/"
runtag <- "ukb-s80.45-adi"
simutags <- paste(8, 1, sep = "-")

configtag <- 1
susiefs <- paste0(outputdir, runtag, "_simu", simutags, "_config", configtag, ".susieIrss.txt")
pfs <- paste0(outputdir, runtag, "_simu",simutags)
gwasfs <- paste0(pfs, ".exprgwas.txt.gz")
phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
#scatter_plot_PIP_p(phenofs, susiefs, gwasfs, main ="PIP-p")
```
Zoom in view
```{r sim 3, out.width = "98%", out.height="95%"}
chrom <- 1
rtag <- 1
plot_all(susiefs[rtag], pfs[rtag], phenofs[rtag], chrom, thin = 0.01)
```
```{r sim 2, out.width = "98%", out.height="95%"}
configtag <- 2
susiefs <- paste0(outputdir, runtag, "_simu", simutags, "_config", configtag, ".susieIrss.txt")
pfs <- paste0(outputdir, runtag, "_simu",simutags)
gwasfs <- paste0(pfs, ".exprgwas.txt.gz")
phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
#scatter_plot_PIP_p(phenofs, susiefs, gwasfs, main ="PIP-p")

chrom <- 1
rtag <- 1
plot_all(susiefs[rtag], pfs[rtag], phenofs[rtag], chrom, thin = 0.01)
```

```{r rerun}
#a <- plot_region(runtag, simutags[1], configtag, chr = 1, startpos = 222230220 , endpos = 224938520 ,  plot_ceqtl = T, rerun_ctwas = T)

load(phenofs[1])
cau <- get_causal_id(phenores)
load("~/temp2.Rd")
susieres <- susie_rss(z, R, z_ld_weight = z_ld_weight, 
                  L = L, prior_weights = prior, null_weight = nw, 
                  prior_variance = V, estimate_prior_variance = F, 
                  coverage = coverage)
load("~/temp1.Rd")
outdf.reg <- ctwas:::anno_susie(susieres, geneinfo, snpinfo, gidx, sidx , 1, 1)

a <- plot_region(runtag, simutags[1], configtag, chr = 1, startpos =32438685 , endpos = 34799758,  plot_ceqtl = T, rerun_ctwas = T)

```
